---
title: "Homework 2"
author: Benjamin Anderson II
format: pdf
---

```{r setup}
#| message: false
#| warning: false
library(tidyverse)
```

Tasks that require an answer are bolded (inside `**` in the .Rmd file). For any task that includes a question (i.e. it ends with "?"), you should also answer the question in sentence form.

# Looking at Data

The following tasks all relate to the dataset `starwars` that comes with the dplyr package. Since, dplyr is included in the tidyverse, you don't need to import this data, just type its name to see it:

```{r}
starwars
```

It contains attributes of the characters in *some* of the Star Wars films. You can find out more about the variables by examining the help page:

```{r}
#| eval: false
?starwars
```

## 1.

**How many rows and columns does the dataset `starwars` have?** *(Use the output from the above chunk to answer this question)* (1pt)

```{r}
nrow(starwars)
ncol(starwars)
```

There are 87 rows and 14 columns.

## 2.

The following code extracts the characters from the starwars data are not human and saves the result to a variable called `not_humans`.

```{r}
not_humans <- filter(starwars, species != "Human")
```

**How many non-human characters are in the dataset?** (2pts) (*Your answer should include code, relevant output, and a complete sentence answer to the question.*)

```{r}
paste("There are", nrow(not_humans), "non-humans in the data set.", sep = " ")
```

## 3.

**Create a scatterplot of all (human and non-human) characters' mass against their height, using color to represent sex.** (2pts)

```{r}
ggplot(data = starwars, mapping = aes(x = height, y = mass)) + 
  geom_point(mapping = aes(color = sex))
```

## 4.

**Make a scatter plot of the non-human characters mass against their height.** (1pt)

```{r}
ggplot(data = not_humans, mapping = aes(x = height, y = mass)) + 
  geom_point()
```

## 5.

**Make a barchart of all (human and non-human) characters' eye colors.** (1pt)

```{r}
ggplot(data = starwars, mapping = aes(x = eye_color)) + 
  geom_bar()
```

## 6.

**Make a histogram of all (human and non-human) character's mass.** (1pt)

```{r}
ggplot(data = starwars, mapping = aes(x = mass)) + 
  geom_histogram()
```

------------------------------------------------------------------------

(2pts) For correct `author` in header, and submitting both PDF and Quarto files.
